---
title: "DrexelRSeminarSummer21Week6MachineLearning"
author: "Eric Brewe"
date: "8/18/2021"
output: html_document
---

The challenge for this week is to use prinicples of machine learning to find the "Best"  model for predicting post score.  

I'll follow the Tidymodels page and see how it goes.

```{r setup, include=FALSE}
pacman::p_load(here, tidyverse, lubridate, lsr, tidymodels, parsnip, tayloRswift, rsample)

FullData = readRDS(file = "data/CleanTestDataWithLunch.Rda")

```

```{r PrePlotting}

FullData %>%
  select(-ID) %>%
  na.omit(Post) %>%
  ggplot(aes(x = Post, y =  Q1, col = Lunch)) +
  geom_point() + 
  geom_smooth(method = lm, se = FALSE) +
  scale_color_taylor()

```

```{r SetModel}

lm_mod<- linear_reg() %>% set_engine("lm")

lm_fit<- lm_mod %>%
  fit(Post ~ ., data= FullData)

tidy(lm_fit)

```

```{r TryBayes}

prior_dist <- rstanarm::normal(location = 10, autoscale = TRUE)

set.seed(327)

bayes_mod <- 
  linear_reg() %>%
  set_engine("stan",
             prior_intercept = prior_dist,
             prior = prior_dist)

bayes_fit <- 
  bayes_mod %>%
  fit(Post ~ ., data = FullData)

library(broom.mixed)
tidy(bayes_fit)

```


```{r split_into_training_test}

library(rsample)
set.seed(327)

data_split <- initial_split(FullData, prop = 3/4)

train_data <- training(data_split)
test_data <- testing(data_split)
```




I don't get the idea of recipes, but I'll follow along because I think the people that wrote the package are really smart. 

```{r CreateRecipe}

post_recipe <-
  recipe(Post ~ .,  data = train_data) %>%
  update_role(ID, new_role = "ID") %>%
  step_dummy(Lunch)

post2_recipe <-
  recipe(Post ~ Q1 + Q2 + ID + Lunch,  data = train_data) %>%
  update_role(ID, new_role = "ID") %>%
  step_dummy(Lunch)

```


Set up the workflow 
```{r SetWorkflow}

post_workflow <- 
  workflow() %>%
  add_model(lm_mod) %>%
  add_recipe(post_recipe)

post2_workflow <- 
  workflow() %>%
  add_model(lm_mod) %>%
  add_recipe(post2_recipe)

```


```{r FitModelToTrainingData}

post_fit <-
  post_workflow %>%
  fit(data = train_data)

tidy(post_fit)

post2_fit <-
  post2_workflow %>%
  fit(data = train_data)

tidy(post2_fit)
```

Now that we have built a model, we can test it out on our test data and merge it back into the test data frame. 
```{r PredictOnTestData}

Pred_data <- predict(post_fit, test_data)

Eval_Mod <- tibble(Post = test_data$Post, Pred = Pred_data$.pred)

#Build up Mean Squared Error and Mean Absolute Errors to evaluate 
Eval_Mod %>%
  filter(Post != "NA", Pred != "NA") %>%
  mutate(raw_diff = Post - Pred) %>%
  mutate(raw_diff_sq = raw_diff**2) %>%
  mutate(raw_diff_abs = abs(raw_diff)) %>%
  summarise(MSE = mean(raw_diff_sq), MAE = mean(raw_diff_abs))

Pred2_data <- predict(post2_fit, test_data)

Eval_Mod2 <- tibble(Post = test_data$Post, Pred = Pred2_data$.pred)

Eval_Mod2 %>%
  filter(Post != "NA", Pred != "NA") %>%
  mutate(raw_diff = Post - Pred) %>%
  mutate(raw_diff_sq = raw_diff**2) %>%
  mutate(raw_diff_abs = abs(raw_diff)) %>%
  summarise(MSE = mean(raw_diff_sq), MAE = mean(raw_diff_abs))

```



